---
title: "Documentation Template"
author: "David Keyes // R for the Rest of Us"
output: 
    html_document:
        css: css/style.css
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
library(tidyverse)
```

# Overview

Explain sample dataset used throughout project

# Projects

## Project Organization

- Use data/data-raw structure

## Workflow

- Break up data cleaning (R script) and reporting (RMarkdown)

## Codebooks 

Explain that R doesn't have variable/value labels like in SPSS

- https://rubenarslan.github.io/codebook/

# Code Style

- Spaces between things
- Line breaks

# Packages

I am a huge proponent of the [tidyverse](https://tidyverse.org/). This 


# Data Import

- clean_names() function

# Data Wrangling and Analysis

# Data Visualization

## Themes

# Tables

- flextable
- gt    
- DT
- formattable
- kable
- kableextra
- huxtable (?)

# Mapping

- tmap
- leaflet
- ggplot 
- mapview

# Reporting

## What format do we knit to?

- When to use HTML?
- xaringan for presentations

## Word

- Using Word reference documents for style

# Collaboration

## Windows Network Drive, Sharepoint, etc.

## Google Drive, Dropbox, etc.

Pluses

- Easy

Minuses

- Only one person can work at a time
- No version control

## Git/GitHub

Pluses

- Hard to get set up

Minuses

- Multiple people can work at a time
- Version control

# Misc to categorize

- https://whattheyforgot.org/


